Nail: A practical interface generator for data formats

### 2014-04-02 paper/eval.tex
figure 4 spacing
spurious space
improve figure placement

\begin{figure*}
\begin{minipage}{0.45\paperwidth}
\begin{verbatim}
utfstring = many choose {
  SUPP = {
    lead  uint16 |  0xD800..0xDBFF
    trail uint16 |  0xDC00..0xDFFF
  }
  BASIC = uint16 | !0xD800..0xDFFF
}
\end{verbatim}
\end{minipage}
~
\begin{minipage}{0.45\paperwidth}
\begin{verbatim}
struct utfstring {
  struct {
    enum { SUPP, BASIC } N_type;
    union {
      struct {
        uint16_t lead;
        uint16_t trail;
      } SUPP;
      uint16_t BASIC;
    };
  } *elem;
  size_t count;
};
\end{verbatim} 
\end{minipage}
\caption{Nail grammar (left) and data model (right) for UTF-16 strings.}
\label{fig:utf16}
\end{figure*}

\begin{figure}
\begin{verbatim}
labels = <many { @length  uint8 | 1..255 
                 label n_of @length uint8 }
          uint8 = 0>

question = {
  labels labels
  qtype uint16 | 1..16 
  qclass uint16 | [1,255]
}

answer = {
  labels labels
  rtype uint16 | 1..16
  class uint16 | [1]
  ttl uint32
  @rlength uint16 
  rdata n_of @rlength uint8 
}

dnspacket = {
  id uint16
  qr uint1
  opcode uint4
  aa uint1 
  tc uint1
  rd uint1
  ra uint1
  uint3 = 0
  rcode uint4
  @qc uint16
  @ac uint16
  uint16 = 0    // authority 
  uint16 = 0    // additional
  // We don't support authority or 
  // additional sections in the prototype
  questions n_of @qc question
  responses n_of @ac answer
}
\end{verbatim}
\caption{Nail grammar for DNS packets, used by our prototype DNS server.}
\label{fig:dns-full}
\end{figure}

>>>>

\input{fig-dnsfull}
